### 2017-01-04 README.Rmd
merged with master
From: Laurent <lg390@cam.ac.uk>

git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MSnbase@125626 bc3139a8-67e5-0310-9ffc-ced21a209358

[![Build Status](https://travis-ci.org/lgatto/MSnbase.svg?branch=master)](https://travis-ci.org/lgatto/MSnbase) [![codecov.io](https://codecov.io/github/lgatto/MSnbase/coverage.svg?branch=master)](https://codecov.io/github/lgatto/MSnbase?branch=master)

>>>>

[![Build Status](https://travis-ci.org/lgatto/MSnbase.svg?branch=master)](https://travis-ci.org/lgatto/MSnbase) 
[![codecov.io](https://codecov.io/github/lgatto/MSnbase/coverage.svg?branch=master)](https://codecov.io/github/lgatto/MSnbase?branch=master)
[![Bioconductor devel build Status](http://bioconductor.org/shields/build/devel/bioc/MSnbase.svg)](http://bioconductor.org/packages/devel/bioc/html/MSnbase.html) 
[![Test coverage](https://bioconductor.org/shields/coverage/devel/MSnbase.svg)](https://codecov.io/github/Bioconductor-mirror/MSnbase/branch/master)
